Measurement of a dwarf galaxy rotational velocity from its Lyman-alpha line emission

### 2016-02-10 paper/letter.tex
paragraph on LARS

2. [General paragrph about the expected Lyman-alpha emission]. Almost
fifty years ago \cite{PartridgePeebles} it was realized that young
galaxies should have a strong Lyman-$\alpha$ line emission. 
This theoretical prediciotn was only confirmed XX year later. 
Currently, Lyman Alpha Emitting galaxies are commonly measure in
surveys.

3. [The link betwween high-z galaxies and lyman alpha, LARS]

4. [Observations require interpretation, common features and
  models]. The Lyman-$\alpha$ line is resonant. A yman-$\alpha$ photon
will follow a difussion-like process before escaping the galaxy or
being absorbed by dust. This makes it hard to interpret Lyman-alpha
line observations as the reulting profile is sensitive to the
dynamical, chemical and thermal conditions in the interstellar
medium. State-of-the-art models

5. [Rotation and the expected features.]
It has been shown that rotation also imprints an effect on the
Lyman-alpha morphology. 
The most important consequence of rotation is that spherical 
symmetry is broken.
The line morphology now depends on the viewing angle respect to the
rotation axis.  
For a line of sight perpendicular to the rotation axis the intensity
and the line center and the line width increase with rotational
velocity.  
When the rotational velocity is close to the half-line width of the
static line, the line becomes single peaked as it is observed in
\tol, a unique feature that other theoretical models find
impossible to reproduce.

6. [The charachteristics of the dwarf galaxy of interest as a puzzling
system]

@@

7. [The results of the fit + Physical picture using other results]

@@

8. [Possible interpretation of this results]

9. [Implications for outflow+rotation in existing samples.]

10. [Future outlook]

>>>>

2. [General paragrph about the expected Lyman-alpha emission,
  LARS]. Almost fifty years ago \cite{PartridgePeebles} it was
realized that young galaxies could be detected through a stron
Lyman-$\alpha$ line emission.  This theoretical prediction was only
confirmed XX year later. 
Currently, Lyman Alpha Emitting galaxies are commonly measure in
surveys. 
The presence of this line provides confirmation of the distance of a
galaxy and also provides clues about the stellar population powering
the emission.

Lyman alpha emission is not exclusive of high redshift galaxies. It
does, require a low dust content to avoid complete extinction and an
source of ionizing radiation.  This has motivated the creation of
local Universe surveys to perform a detailed study of the Lyman-alpha
emission \cite{LARS}. A nearby simple permits the study of other
indicators that might be more difficult to obtain for distant galaxies
such as morphology, dust attenuation, neutral hydrogen contents and
ionization state.

3. [Observations require interpretation, common features and
  models]. The Lyman-$\alpha$ line is resonant. A yman-$\alpha$ photon
will follow a difussion-like process before escaping the galaxy or
being absorbed by dust. This makes it hard to interpret Lyman-alpha
line observations as the reulting profile is sensitive to the
dynamical, chemical and thermal conditions in the interstellar
medium. State-of-the-art models use mon

4. [Rotation and the expected features.]
It has been shown that rotation also imprints an effect on the
Lyman-alpha morphology. 
The most important consequence of rotation is that spherical 
symmetry is broken.
The line morphology now depends on the viewing angle respect to the
rotation axis.  
For a line of sight perpendicular to the rotation axis the intensity
and the line center and the line width increase with rotational
velocity.  
When the rotational velocity is close to the half-line width of the
static line, the line becomes single peaked as it is observed in
\tol, a unique feature that other theoretical models find
impossible to reproduce.

5. [The charachteristics of the dwarf galaxy of interest as a puzzling
system]

@@

6. [The results of the fit + Physical picture using other results]

@@

7. [Possible interpretation of this results]

8. [Implications for outflow+rotation in existing samples.]

9. [Future outlook]
